Trends of SDR in Thessaloniki

### 2023-07-12 Article.Rmd
Commit 2023-07-12 22:10

For completeness, we will provide a brief overview of the CSid process along with the site specific thresholds.
As SDR clear sky reference we are using the radiation model by Haurwitz’s, adjusted for our site with the factor  $a = `r signif(alpha,3)`$ (Eq.\ \ref{eq:ahau}), resulted by an iterative optimization process.
The selection of this clear sky reference model, was based on SDR observations from the period 2016 – 2021.
Where, after an iterative optimization between eight simple models (Daneshyar–Paltridge–Proctor, Kasten–Czeplak, Haurwitz, Berger–Duffie, Adnot–Bourges–Campana–Gicquel, Robledo-Soler, Kasten and Ineichen-Perez) with a wide range factors, we found, that Haurwitz’s model, adjusted with a factor of `r signif(alpha,3)` has one of the lowest root mean squared error (RMSE), while retains most of our data (Eq.\ \ref{eq:ahau}). 
The tried models are described in more details by @Reno2012 and tested by @Reno2016.
The iterative optimization method, for the selection of the reference is described by @Long2000 and @Reno2016.
The target of the optimization was the minimization of the function $f(a)$ (Eq.\ \ref{eq:minf}) and was accomplished by the computing function `stats::optimise` [@RCT2023], which is based on work by @Brent1973.

>>>>

For completeness, we will provide a brief overview of the CSid process, along with the site specific thresholds.
As a reference clear sky SDR, we are using the radiation model by Haurwitz’s, adjusted for our site with the factor $a = `r signif(alpha,3)`$ (Eq.\ \ref{eq:ahau}), resulted by an iterative optimization process, as described by @Long2000 and @Reno2016.
The target of the optimization was the minimization of the function $f(a)$ (Eq.\ \ref{eq:minf}) and was accomplished with the computing function `stats::optimise` [@RCT2023], which is based on work by @Brent1973.
The optimization and the selection of the clear sky reference model, was performed on SDR observations for the period 2016 – 2021.
During the optimization, eight simple clear sky radiation models were tested (Daneshyar–Paltridge–Proctor, Kasten–Czeplak, Haurwitz, Berger–Duffie, Adnot–Bourges–Campana–Gicquel, Robledo-Soler, Kasten and Ineichen-Perez), with a wide range of factors. We found, that Haurwitz’s model, adjusted with the factor $a = `r signif(alpha,3)`$ has one of the lowest root mean squared error (RMSE), while correlates with large amount of our data. Thus, our clear sky reference is the Eq.\ \ref{eq:ahau}. 
The tried models are described in more details by @Reno2012 and evaluated by @Reno2016.
